---
title: "ElectricVisual"
output: github_document
---

# ElectricVisual

ElectricVisual is an R package designed for visualization and analysis of electricity data. It provides functions for importing, preprocessing, and visualizing data from electric companies, enabling professionals in the energy sector to explore and interpret electricity data efficiently.

## Installation

You can install ElectricVisual from CRAN using the following command:

```{r}

install.packages("ElectricVisual")

```

Alternatively, you can install the development version from GitHub:

```{r}

devtools::install_github("OnceTw1031/Sp24_LIS4370")

```

Usage

```{r}

library(ElectricVisual)

# Example usage of import_data function
data <- import_data("electric_data.csv")

# Example usage of preprocess_data function
clean_data <- preprocess_data(data)

# Example usage of plot_timeseries function
plot_timeseries(clean_data, time_column = "timestamp", value_column = "consumption")

# Example usage of plot_histogram function
plot_histogram(clean_data, value_column = "consumption", bins = 20)

```

Features and Functionalities
  Importing electricity data from CSV or Excel files.
  Preprocessing data to handle missing values and outliers.
  Visualizing time series data with customizable plots.
  Visualizing data distributions with histograms.


License Information
ElectricVisual is released under the MIT License.