---
title: "Importing Data with ElectricVisual"
author: "Isabelle Bolen"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Introduction

The `import_data` function in the ElectricVisual package is designed to facilitate the importing of data files into R for analysis. This vignette provides an overview of the function and demonstrates its usage with various types of data files.

# Function Overview

The `import_data` function allows users to import data from CSV, Excel, or other common file formats into R. It automatically detects the file format and imports the data into a data frame for further analysis.

## Usage

The basic syntax for using the `import_data` function is as follows:

```{r}
data <- import_data(file_path)
```

Here are some examples demonstrating how to use the import_data function with different types of data files:

```{r}
# Importing a CSV File
data <- import_data("path/to/your/csv/file.csv")

# Importing an Excel File
data <- import_data("path/to/your/excel/file.xlsx")

```

After importing the data using the import_data function, users may need to perform additional preprocessing steps depending on the specific characteristics of the data.
