---
title: "Plotting Time Series Data with ElectricVisual"
author: "Isabelle Bolen"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Introduction

The `plot_timeseries` function in the ElectricVisual package is designed to visualize time series data in R. This vignette provides an overview of the function and demonstrates its usage with different time series datasets.

# Function Overview

The `plot_timeseries` function allows users to create various types of plots for time series data, including line plots, area plots, and scatter plots.

## Usage

The basic syntax for using the `plot_timeseries` function is as follows:

```{r}

plot_timeseries(data, time_column, value_column)

```

Here are some examples demonstrating how to use the plot_timeseries function with different time series datasets:

```{r}

# Line plot
plot_timeseries(data, time_column = "timestamp", value_column = "value", type = "line")

# Area plot
plot_timeseries(data, time_column = "date", value_column = "sales", type = "area")

```

The plot_timeseries function supports various visualization techniques, including:

Line plots
Area plots
Scatter plots
These techniques can help users visualize trends, patterns, and anomalies in their time series data.