---
title: "Visualizing Data Distributions with ElectricVisual"
author: "Isabelle Bolen"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Introduction

The `plot_histogram` function in the ElectricVisual package is designed to visualize the distribution of a single variable in R. This vignette provides an overview of the function and demonstrates its usage with different datasets.

# Function Overview

The `plot_histogram` function allows users to create histograms to visualize the distribution of a single variable in their datasets.

## Usage

The basic syntax for using the `plot_histogram` function is as follows:

```{r}

plot_histogram(data, value_column)

```

Here are some examples demonstrating how to use the plot_histogram function with different datasets:

```{r}

# Basic histogram
plot_histogram(data, value_column = "age")

# Customizing histogram appearance
plot_histogram(data, value_column = "height", bins = 20, color = "blue", title = "Height Distribution")

```

The plot_histogram function supports various visualization techniques, including:

Adjusting the number of bins
Customizing colors and titles
Adding axis labels
These techniques can help users explore and analyze the distribution of their data effectively.