---
title: "Data Preprocessing with ElectricVisual"
author: "Isabelle Bolen"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Introduction

The `preprocess_data` function in the ElectricVisual package is designed to preprocess and clean data imported into R using the `import_data` function. This vignette provides an overview of the function and demonstrates its usage with different datasets.

# Function Overview

The `preprocess_data` function allows users to perform various preprocessing steps on imported data, such as handling missing values, filtering rows or columns, and transforming variables.

## Usage

The basic syntax for using the `preprocess_data` function is as follows:

```{r}

clean_data <- preprocess_data(data)

```

Here are some examples demonstrating how to use the preprocess_data function with different datasets:

```{r}

# Handling missing values
clean_data <- preprocess_data(data, method = "remove_na")

# Filtering rows or columns
clean_data <- preprocess_data(data, rows = c(1, 3, 5), columns = c("var1", "var2"))

```

The preprocess_data function performs various preprocessing steps, including:

Handling missing values
Filtering rows or columns
Transforming variables
These steps are essential for ensuring that the data is clean and ready for analysis.